Summary of cell type ontologies in reference files

### 2025-08-20 analyses/cell-type-consensus/exploratory-notebooks/06-update-consensus-scimilarity.Rmd

Previously when we looked at the LCA for pairs with moret than 1 match, we had seen only very broad cell types. 
That doesn't seem to be the case here as we see things like "memory T cell".

Perhaps instead of just removing the pairs with multiple LCA, we first filter out the terms that don't meet our criteria. 
Then if multiple LCA remain we find the LCA of all the remaining LCA's and if that new LCA meets our criteria we use that instead.

@@

```{r}
# firt get a dataframe of the matches we will keep that had multiple LCA and their final annotations
multi_lca_keep_df <- new_lca_df |> 
  dplyr::filter(total_descendants <= 170 & cl_annotation != "epithelial cell of nephron" | cl_annotation == "kidney tubule cell") |> 
  dplyr::select(id1, id2, id1_annotation, id2_annotation, lca = updated_lca, cl_annotation, total_descendants) |> 
  unique()
```

>>>>

Previously, when we looked at the LCA for pairs with more than 1 match, we had seen only very broad cell types. 
That doesn't seem to be the case here as we see things like "memory T cell".

Perhaps instead of just removing the pairs with multiple LCA, we first filter out the terms that don't meet our criteria. 
Then, if multiple LCAs remain, we find the LCA of all the remaining LCAs, and if that new LCA meets our criteria, we use that instead.

@@

```{r}
# first get a data frame of the matches we will keep that had multiple LCA and their final annotations
multi_lca_keep_df <- new_lca_df |> 
  dplyr::filter(total_descendants <= 170 & cl_annotation != "epithelial cell of nephron" | cl_annotation == "kidney tubule cell") |> 
  dplyr::select(id1, id2, id1_annotation, id2_annotation, lca = updated_lca, cl_annotation, total_descendants) |> 
  unique()
```
